Case study validations of automatic bullet matching

### 2018-11-27 index.Rmd

```{r b2b, echo = FALSE, fig.width = 9, fig.height = 5,  out.width='.6\\textwidth', fig.cap="Overview of land-land matching scores for two pairs of bullet-bullet comparisons. On the left the two bullets are known to come from the same source (barrel) on the right, the bullets are from two different sources (barrels)"}
grid.arrange(p1, p2, ncol = 2, padding = 2)
```

>>>>

```{r b2b, echo = FALSE, fig.width = 5.4, fig.height = 3, out.width = ".6\\textwidth", fig.cap="Overview of land-land matching scores for two pairs of bullet-bullet comparisons. On the left the two bullets are known to come from the same source (barrel) on the right, the bullets are from two different sources (barrels)"}
grid.arrange(p1, p2, ncol = 2, padding = 2)
```
